### 2020-01-30 wuhan.tex
Title

\begin{flushleft}{
	\Large
	\textbf\newline{
		Evaluating uncertainties associated with preliminary estimates of the basic reproductive number during the novel coronavirus (2019-nCoV) outbreak
	}
}

@@

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Reconciling early-outbreak preliminary estimates of the basic reproductive number: a new framework and applications to the novel coronavirus (2019-nCoV) outbreak
	}
}

@@

We have provided a basis for evaluating and comparing exponential-growth based estimates of \Ro\ in terms of three simple components. We are hopeful that this will provide a guide to understanding and reconciling different estimates early in an epidemic.
